Ms 1

### 2017-08-08 ms1/ms1_display.Rmd
new dxrx

```{r claims_by_age}
read_tsv('tables/claims_by_age_group.tsv') %>%
  mutate(cpkp=round(cpkp)) %>%
  select(year, age_group, cpkp) %>%
  spread(year, cpkp) %>%
  kable
```

>>>>

```{r claims_by_age}
read_tsv('tables/claims_by_age.tsv') %>%
  mutate(age_group=case_when(between(.$age, 65, 75) ~ '65-75',
                             between(.$age, 76, 85) ~ '76-85',
                             between(.$age, 86, 95) ~ '86-95')) %>%
  group_by(year, age_group) %>%
  summarize_at(vars(n_bene, n_claims), sum) %>%
  ungroup() %>%
  mutate(cpkp=round(1000*n_claims/n_bene)) %>%
  select(year, age_group, cpkp) %>%
  spread(year, cpkp) %>%
  kable
```
